---
title: "Homework 3"
author: "Aditi Nachnani"
date: "2/19/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#### Due: 2/17/2022 before 11:59pm. Submit in Canvas (file upload).
1. b. In the RMarkdown file, write down team members, and their github repository links;  
the number of successful pull requests you made, and the github repository to which you requested a change;  
the number of pull requests you accepted, and the github repository from which you accepted.  

Team member names and their github repository links:
- Tara Munjuluri: https://github.com/TaraMunjuluri/practice1-TaraMunjuluri.git
- Snehal Arla: https://github.com/AditiN2003/practice1-Snehal2301.git 
    https://github.com/Snehal2301/Graph.git
- Aditi Nachnani: https://github.com/AditiN2003/practice1-aditin2003.git
 number of pull requests you accepted and number of successful pull requests you made: 2
 github repository to which you requested a change and the github repository from which you accepted: practice1-TaraMunjuluri and practice1-Snehal2301
 
 c. Write down a list with at least 3 tips of how to make working with git/github easier 
 - watch videos on how to work git/github
 - ask friends if lost
 - make sure you make a commit after making a change

2. Generate the graph of LifExp vs. gdpPercap for US, Canada (fixed data) and Australia by RMarkdown based on the data set "gapminder-5060", like what we did in the class.  
```{r}
gapMinder <- read.csv("gapminder-5060.csv")
```
```{r}
summary(gapMinder)
```
```{r}
subset_gapMinder <- subset(gapMinder, country %in% c( "Canada","Australia","United States"))

```


```{r}
library(ggplot2)
ggplot(data = subset_gapMinder, aes(x = lifeExp, y = gdpPercap)) +
  geom_point(aes(color = country))+
   labs(title = "Life Expectancy vs. GDP per capita by Country",
       x = "Life Expectancy",
       y = "GDP per capita") +
  scale_color_manual(values = c("#0072B2", "#D55E00", "#009E73")) +
  scale_x_continuous(limits = c(0, 120)) +
  scale_y_continuous(limits = c(100, 20000))
```

 
 3. Write a paragraph (~200 words) describing an example of what you consider data science. Write your paragraph in R Markdown. Include at least 
    a. one link to a chart or an image and 
    b. at least one itemized or enumerated list.
    
    One example of data science is the analysis of social media data to gain insights into consumer behavior. Social media platforms like Twitter, Facebook, and Instagram generate vast amounts of data every day. With the help of data science techniques, this data can be processed and analyzed to provide valuable insights. For instance, a company may want to analyze how its brand is perceived on social media or which types of content are most popular among its target audience.

As an example, consider the following chart: https://www.statista.com/statistics/203513/usage-trands-of-social-media-platforms-in-marketing/

Some steps involved in data science include:

    - Data collection: Gathering data from various sources such as APIs, databases, or web scraping.
    - Data cleaning and preprocessing: Processing and cleaning data to remove noise, inconsistencies, and errors.
    - Exploratory data analysis: Conducting statistical analyses, visualization, and data exploration to identify patterns and relationships in the data.
    - Building and evaluating models: Creating models to make predictions and evaluating their performance using statistical measures.
    - Communicating insights: Presenting the results of data analysis using visualization, reports, and presentations to stakeholders.